Hierarchical wrinkling in a confined permeable biogel

### 2015-01-22 fig_plis/article_plis.tex
Use data from ech23 and ech25 Little pore size change in half coat. Thick lines

\begin{figure}[ht!]
	\includegraphics{dynamics}
	\caption{Dynamics of pattern formation in a confined film of casein gel (caseinate 4\%w, GDL 4\%w). (a) Light transmission microscopy. The same area is highlighted in yellow on all panels to show that the initial pattern is not evolving. (b) 3D reconstruction from fluorescent confocal microscopy. (c) Fourier spectra of binary altitudes of (a) corresponding to primary, secondary and tertiary patterns. Inset: reconstructed binary altitudes at time \SI{2}{\hour}. Scale bars are \SI{1}{\milli\metre}.}
	\label{fig:dynamics}
\end{figure}

@@

\begin{figure}[b]
	\includegraphics{acidification}
	\caption{Acid-induced protein gel properties behave nonmonotonically with pH. (a) pH decrease over time in a 4\%w sodium caseinate solution acidified by 4\%w GDL. The horizontal line indicates isoelectric pH of casein. (b) Evolution of the storage modulus $G'$ measured in a rheometer with full adhesion to rotor and stator. (c) Evolution of pore size measured by confocal microscopy in a half-coated microscopy cell with no adhesion to top wall, syn\ae{}resis and swelling allowed.}
	\label{fig:acidification}
\end{figure}

@@

The slow acidification of a protein (sodium caseinate) solution down to the isoelectric pH induces gelation~\cite{Bremer1989} (Fig.~\ref{fig:acidification}a). Since caseins strongly adsorb to interfaces, the resulting gel sticks to the container walls, allowing rheological measurements (Fig.~\ref{fig:acidification}b). Further decrease of the pH beyond the isoelectric point makes the casein aggregates swell (Supplemental Fig.~\ref{fig:nonmonotonic}), thus weakening the gel~\cite{Braga2006}. In a microscopy cell of slit geometry coated so that the casein cannot adsorb on the top wall, this microscopic nonmonotonic behaviour translates into solvent expulsion out of the gel phase (syn\ae{}resis) followed by global swelling (Fig.~\ref{fig:acidification}c and Supplemental Fig.~\ref{fig:nonmonotonic}).

>>>>

\begin{figure}[ht!]
	\includegraphics{dynamics}%
	\caption{Dynamics of pattern formation in a confined film of casein gel (caseinate 4\%w, GDL 4\%w). (a) Light transmission microscopy. The same area is highlighted in yellow on all panels to show that the initial pattern is not evolving. (b) 3D reconstruction from fluorescent confocal microscopy. (c) Fourier spectra of binary altitudes of (a) corresponding to primary, secondary and tertiary patterns. Inset: reconstructed binary altitudes at time \SI{2}{\hour}. Scale bars are \SI{1}{\milli\metre}.}%
	\label{fig:dynamics}%
\end{figure}

@@

\begin{figure}[b]
	\includegraphics{acidification}%
	\caption{Acid-induced protein gel properties behave nonmonotonically with pH. (a) pH decrease over time in a 4\%w sodium caseinate solution acidified by 4\%w GDL. The horizontal line indicates isoelectric pH of casein. (b) Evolution of the storage modulus $G'$ measured in a rheometer with full adhesion to rotor and stator. (c) Evolution of pore size measured by confocal microscopy in a slit geometry with either adhesion to all walls (black line) or no adhesion to top wall, i.e. allowed syn\ae{}resis and swelling (orange dashed line).}%
	\label{fig:acidification}%
\end{figure}

@@

The slow acidification of a protein (sodium caseinate) solution down to the isoelectric pH induces gelation~\cite{Bremer1989} (Fig.~\ref{fig:acidification}a). Since caseins strongly adsorb to interfaces, the resulting gel sticks to the container walls, allowing rheological measurements (Fig.~\ref{fig:acidification}b). Further decrease of the pH beyond the isoelectric point makes the casein aggregates swell (Supplemental Fig.~\ref{fig:nonmonotonic}), thus weakening the gel~\cite{Braga2006}. In a microscopy cell of slit geometry coated so that the casein cannot adsorb on the top wall, this microscopic nonmonotonic behaviour translates into little variation of the pore size $\xi$ but to solvent expulsion out of the gel phase (syn\ae{}resis) followed by global swelling (Fig.~\ref{fig:acidification}c and Supplemental Fig.~\ref{fig:nonmonotonic}).
